Assigning Boy Scouts to Patrols

### 2016-06-02 poster/poster.tex
Added to poster file
Simplifications and Acknowledgements

\begin{frame}{Simplifications}
	\begin{itemize}
		\item Instead of considering the scouts' complex personality and their interactions with other scouts, we simplified by only asking each scout which other scouts they liked or disliked.

		\item Add last simplification
	\end{itemize}
\end{frame}

% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{A Mathematical Interpretation}
1 enemy + 1 enemy = 0 survivors  
\end{frame}

@@

>>>>

\begin{frame}{Simplifications}
	\begin{itemize}
		\item Instead of considering the scouts' complex personality and their interactions with other scouts, we simplified by only asking each scout which other scouts they liked or disliked.
		\vspace{0.5in}
		\item Quality of the a patrol can be determined by the quality of the relationships between the unique pairs of the group. \\
		\textbf{i.e.} the whole is equal to the sum of its parts.
	\end{itemize}
\end{frame}

\begin{frame}{Acknowledgments}
	We would like to sincerely thank:
	\vspace{0.2in}
	\begin{itemize}
		\item \textbf{Scoutmaster Gene Bruce} for providing us the data and being extremely patient and understanding when discussing the background and problem.
		\vspace{0.2in}
		\item \textbf{Professor Sara Billey} for the mentorship and guidance throughout the entire project.
		\vspace{0.2in}
		\item \textbf{Austin Tran} for his helpful comments and suggestions.
	\end{itemize}
\end{frame}
% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{A Mathematical Interpretation}
1 enemy + 1 enemy = 0 survivors  
\end{frame}

@@

\begin{frame}{}
    \begin{block}{How Good Are These Solutions?}
\begin{figure}[h]
    \centering
    \begin{tabular}{ |l|l|l|l| }
        \hline
        \textbf{Method} & \textbf{MinCut} & \textbf{FriendCut} & \textbf{EnemyCut} \\
        \hline
        MinCut & 0 & 17 & 0 \\
        FriendCut & 1 & 18 & 1 \\
        EnemyCut & 2 & 15 & 0 \\
        AwkwardCut (+1) & 0 & 17 & 0 \\
        AwkwardCut (+2) & 1 & 18 & 2 \\
        HybridCut & 0 & 18 & 1 \\
        \hline
    \end{tabular}
    \caption{The scores according to the three primary metrics.}
\end{figure}
    \end{block}
\end{frame}
